% places to update: GitHub (release package), /Documents, website, Simplify, Handshake, Monster, Indeed, RippleMatch, LinkedIn

% Document class and font size
\documentclass[letterpaper,10pt]{extarticle}

% FONT: Charter (almost sans serif, narrower)
% \usepackage{lmodern} % font family (lighter)
% \usepackage{charter}
% \fontfamily{bch}\selectfont

% FONT: Helvetica (bolder, bigger sans serif)
\usepackage{helvet} % font family
\fontfamily{phv}\selectfont

% FONT: Computer Modern Sans Serif (thinner, smaller sans serif)
% \fontfamily{cmss}\selectfont

% \usepackage{lmodern}
% \fontfamily{lmss}\selectfont

\renewcommand{\familydefault}{\sfdefault}


% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{letterpaper, margin=0.75in} % Set paper size and margins
% \geometry{a4paper, margin=0.75in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks

% Packages (I Added)
\usepackage{soul} % For highlighting
\usepackage{xcolor} % For color

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing
\setlist[itemize]{leftmargin=5.5mm} % sets left margin to roughly equal
% \setlist[itemize]{leftmargin=*} % removes margin left of bullets

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{empty}

% Header
\begin{center}
\textbf{\Large David Zhan}\\[2pt] % Name
% Albany, CA $|$ Amherst, MA

\href{mailto:zhandavidz@gmail.com}{zhandavidz@gmail.com} $|$ \href{tel:5105080222}{(510) 508-0222}

\href{https://davidzhan.com}{davidzhan.com} $|$ \href{https://www.linkedin.com/in/zhandavidz}{linkedin.com/in/zhandavidz} $|$ \href{https://github.com/zhandavidz}{github.com/zhandavidz}

% \href{mailto:zhandavidz@gmail.com}{zhandavidz@gmail.com} $|$ \href{tel:5105080222}{(510) 508-0222}
% $|$
% \href{https://www.linkedin.com/in/zhandavidz}{linkedin.com/in/zhandavidz} $|$ \href{https://davidzhan.com}{davidzhan.com} $|$ \href{https://github.com/zhandavidz}{github.com/zhandavidz}

\end{center}

% Education Section
\section*{EDUCATION}
\noindent
\textbf{University of Massachusetts Amherst} \hfill Major GPA: 4.0 $|$ \textbf{Overall GPA: 3.98}\\
MS, Computer Science \hfill Expected: Sep 2024 - \textbf{May 2026}\\
BS, Computer Science \hfill Expected: Sep 2022 - May 2025\\

\noindent
\textbf{Relevant Coursework:} Data Structures, Algorithms, ML, Databases, Networking, Game Dev etc.


% % Education Section
% \section*{EDUCATION}
% \noindent
% \textbf{University of Massachusetts Amherst} \hfill Expected: Sep 2024 - \textbf{May 2026}\\
% MS, Computer Science\\


% \noindent
% \textbf{University of Massachusetts Amherst} \hfill Expected: Sep 2022 - May 2025\\
% BS, Computer Science \hfill Major GPA: 4.0 $|$ \textbf{Overall GPA: 3.98}\\
% \textbf{Relevant Coursework:} Data Structures, Algorithms, Machine Learning, Databases, Networking, Game Dev etc.

\section*{EXPERIENCE}

\noindent
\textbf{UMass Amherst | CICS} \hfill Feb 2024 - Present \\
\textit{Undergraduate Course Assistant (Undergraduate TA)}
\begin{itemize}
    \item Grade assignments, teach concepts, help students in computer systems and web development courses.
    \item Prepare for and present lessons, actively facilitating safe learning environment by encouraging questions.
    \item Increased student engagement during discussions, receiving positive feedback from my professor and students.
\end{itemize}


\noindent
\textbf{RadWatch | UC Berkeley} \hfill Jun - Aug 2020, 2021 \\
\textit{Summer Intern / Data Analyst Intern}
\begin{itemize}
    \item Worked on DoseNet, an international sensor network for improving community understanding of radiation.
    \item Implemented and integrated Python scripts and web tools to process and visualize lots of radiation sensor data.
    \item Wrote report on my scripts proposing potential use cases while summarizing and documenting my process.
\end{itemize}

\noindent
\textbf{Academic Talent Development Program} \hfill Jun - Aug 2017, 2019\\ 
\textit{Teaching Assistant: Web Development, Programming in Java}
\begin{itemize}
    \item Analyzed student code, assisted in grading, and led many small groups of students in completing classwork.
    \item Guided groups to better collaborate with each other, be more responsible, and learn on their own.
\end{itemize}


\section*{PROJECTS}
\noindent
\textbf{Blahgenda} \hfill Nov 2022\\
\textit{JavaScript, React.js, HTML/CSS (Bulma/Sass)} \hfill \texttt{\href{https://blahgenda.dzhan.dev}{blahgenda.dzhan.dev}} | \texttt{\href{https://devpost.com/software/blahgenda}{devpost.com/software/blahgenda}}
\begin{itemize}
    \item Winning submission to HackUMass X in the category Best Use of Appwrite.
    \item Collaboratively developed a calendar to maximize user efficiency and glanceability while remaining beautiful.
    \item Designed UI, improved page flow, implemented core features, presented final product to judges.
    \item Built with React.js and Bulma CSS to quickly write efficient and maintainable code within the 36-hour hackathon.
\end{itemize}

\noindent
\textbf{Personal Website} \hfill Oct 2017 - Present\\
\textit{JavaScript, HTML/CSS/Sass, Git, Linux} \hfill \texttt{\href{https://davidzhan.com}{davidzhan.com}} %| \texttt{\href{https://github.com/zhandavidz/personal-website/}{github.com/zhandavidz/personal-website}}
\begin{itemize}
    \item Overhauled a static HTML site to display my programming portfolio, experiences, and contact information.
    \item Applied Sass styling and JavaScript loading to reduce code duplication and improve maintainability.
\end{itemize}


\noindent
\textbf{Artemis} \hfill Nov 2020\\
\textit{Godot Engine, GDScript (similar to Python)} \hfill \texttt{\href{https://itch.io/jam/game-off-2020/rate/840095}{itch.io/jam/game-off-2020/rate/840095}}
\begin{itemize}
    \item Placed in the top half of Game Off 2020, GitHub's annual month-long game jam, with my first game.
    \item Developed the game including code, sound design, and pixel art within one month with no prior experience.
    % \item It's a sci-fi space shooter, where the goal is to survive waves of attacks until you reach the moon.
\end{itemize}


% Skills Section
\section*{SKILLS}
\begin{itemize}
    \item \textbf{Programming:} JavaScript/TypeScript, React.js, Python, Java, C, HTML/CSS/Sass, PostgreSQL, Git/GitHub%, GDScript, {\fontfamily{lmodern}\selectfont \LaTeX}
    %\item \textbf{Software:} Familiarity with Linux, the terminal, Git/GitHub, Godot Engine
    %\item \textbf{Relevant Coursework:} Machine Learning, Databases, Algorithms, Data Structures, Linear Algebra, etc.
    % \item \textbf{General Skills:} Active Listening, Inclusive Collaboration, Problem-Solving, Efficiency Under Pressure
    % \item \textbf{General Skills:} Problem-Solving, Active Listening, Collaboration, Native Chinese Speaker (Mandarin)
    \item \textbf{Languages:} Native English and Chinese (Mandarin) speaker
\end{itemize}

\end{document}
