% Document class and font size
\documentclass[letterpaper,10pt]{extarticle}
\usepackage{lmodern} % font family (lighter)

% new font (almost sans serif, narrower
\usepackage{charter}
\fontfamily{bch}\selectfont

% Packages
\usepackage[utf8]{inputenc} % For input encoding
\usepackage{geometry} % For page margins
\geometry{letterpaper, margin=0.75in} % Set paper size and margins
% \geometry{a4paper, margin=0.75in} % Set paper size and margins
\usepackage{titlesec} % For section title formatting
\usepackage{enumitem} % For itemized list formatting
\usepackage{hyperref} % For hyperlinks

% Packages (I Added)
\usepackage{soul} % For highlighting
\usepackage{xcolor} % For color

% Formatting
\setlist{noitemsep} % Removes item separation
\titleformat{\section}{\large\bfseries}{\thesection}{1em}{}[\titlerule] % Section title format
\titlespacing*{\section}{0pt}{\baselineskip}{\baselineskip} % Section title spacing

% Begin document
\begin{document}

% Disable page numbers
\pagestyle{empty}

% Header
\begin{center}
\textbf{\Large David Zhan}\\[2pt] % Name
Amherst, MA

\href{mailto:dzhan@umass.edu}{dzhan@umass.edu} | \href{tel:5105080222}{(510) 508-0222}

\href{https://www.linkedin.com/in/zhandavidz}{linkedin.com/in/zhandavidz} | \href{https://davidzhan.com}{davidzhan.com} | \href{https://github.com/zhandavidz}{github.com/zhandavidz}
\end{center}

% Education Section
\section*{EDUCATION}
\noindent
\textbf{University of Massachusetts Amherst} \hfill Expected: Sep 2022 - \textbf{May 2025}\\ % University name and location
BS, Computer Science \hfill Overall GPA: 3.96 | Major GPA 4.0\\ % Degree and GPA
Commonwealth Honors College % \hfill Manning College of Information and Computer Sciences

% Experience Section
\section*{EXPERIENCE}
\noindent
\textbf{Albany Hacks 2022} \hfill Apr 2022\\ % Company name and location
\textit{Organizer, Judge} \hfill \texttt{\href{https://albany-hacks-2022.devpost.com/}{albany-hacks-2022.devpost.com}} 
\begin{itemize}
    \item As president of Programming Club, I founded my school's first hackathon and served as an organizer and judge.
    \item Helped fundraise \$200 in prizes, with many guest speakers and workshops throughout the hackathon.
    \item Learned a lot about communication and leading a team to successfully run and organize a large event.
\end{itemize}

\noindent
\textbf{RadWatch | UC Berkeley Dept Nuclear Engineering} \hfill Jun - Aug 2021 \\
\textit{Summer Intern} \hfill Jun - Aug 2020
\begin{itemize}
    \item Worked on DoseNet, an international sensor network for improving community understanding of radiation.
    \item Created and integrated scripts and web tools to process and visualize mass quantities of sensor data.
    \item Learned to communicate and collaborate with a group to improve and add features to an existing project.
    % \item Integrated my tools with the overall project.
\end{itemize}

% Additional Experience or Volunteer Work
\noindent
\textbf{Academic Talent Development Program} \hfill Jun - Aug 2019\\ % Project or organization name and location
\textit{Teaching Assistant: Web Development, Programming in Java} \hfill Jun - Aug 2017 % Position and duration
\begin{itemize}
    % \item Worked as a teaching assistant in the Web Development and Programming in Java classes.
    \item Analyzed student code, assisted in grading, and led my own small group of students in completing classwork.
    \item Learned how to communicate and lead groups to better collaborate with each other and be responsible.
    % \item \hl{finish description}
\end{itemize}

% Club or Organization Experience
% \noindent
% \textbf{Academic Talent Development Program} \hfill Berkeley, CA\\ % Club or organization name and location
% \textit{Office Assistant, Digital Archivist, Volunteer} \hfill September 2017 - October 2017 % Position and duration
% \begin{itemize}
%     \item Scanned old documents for digital archives. Helped with organizing the workspace.
%     \item \hl{finish description}
% \end{itemize}

% Projects Section
\section*{PROJECTS}
\noindent
\textbf{Blahgenda} \hfill Nov 2022\\ % Project name and location
\textit{React.js, Appwrite, HTML/Sass, AWS} \hfill \texttt{\href{https://blahgenda.dzhan.dev}{blahgenda.dzhan.dev}} | \texttt{\href{https://devpost.com/software/blahgenda}{devpost.com/software/blahgenda}}
\begin{itemize}
    \item Winning submission to HackUMass X in the category Best Use of Appwrite.
    \item Is a calendar and scheduler designed to maximize efficiency and glanceability while remaining beautiful.
    \item I worked on styling, UI/UX, and implementing features and the flow of the page.
    \item Learned a lot about React.js, and about working collaboratively in an intense, crunch-time environment.
\end{itemize}

% Additional Project
\noindent
\textbf{Personal Website} \hfill Oct 2017 - Present\\ % Project name and location
\textit{JavaScript, HTML/Sass, Git, Linux} \hfill \texttt{\href{https://davidzhan.com}{davidzhan.com}} %| \texttt{\href{https://github.com/zhandavidz/personal-website/}{github.com/zhandavidz/personal-website}}
\begin{itemize}
    \item Displays current projects, my programming and photography portfolios, and my contact info.
    \item Allows me to experiment with and learn web development, Linux server hosting, and Git version control. %, fostering my interest in programming.
    % \item \hl{finish description}
\end{itemize}

% Additional Project
\noindent
\textbf{Artemis} \hfill Nov 2020\\ % Project name and location
\textit{Godot Engine, GDScript (similar to Python)} \hfill \texttt{\href{https://itch.io/jam/game-off-2020/rate/840095}{itch.io/jam/game-off-2020/rate/840095}}
\begin{itemize}
    \item Solo submission ranking in the top half of Game Off 2020, GitHub's annual month-long game jam.
    % \item It's a sci-fi space shooter, where the goal is to survive waves of attacks until you reach the moon.
    \item Used a game engine for the first time, learning game development and a new language in just 1 month.
    % \item Learned
    % \item \hl{finish description}
\end{itemize}

% Additional Project
% \noindent
% \textbf{Beat Coronavirus} \hfill Apr 2020\\ % Project name and location
% \textit{JavaScript, HTML/CSS} \hfill \texttt{\href{https://devpost.com/software/beat-coronavirus}{devpost.com/software/beat-coronavirus}}
% \begin{itemize}
%     \item Submission to TitanHacks 2020, a 24-hour hackathon, teaching kids ways to stay safe during the pandemic.
%     \item Learned to apply my knowledge and work efficiently to finish a large project within a short deadline.
% \end{itemize}

% Additional Project
% \noindent
% \textbf{Artificial Intelligence Research Project} \hfill Jan - Mar 2018 \\ % Project name and location
% \textit{JavaScript, HTML/CSS} \hfill \texttt{\href{https://davidzhan.com/projects/isearch-ai/}{davidzhan.com/projects/isearch-ai}}
% \begin{itemize}
%     \item Website built under a fictional persona to share my school research on the history and future of AI.
%     \item Learned about the state of and ethics involving AI while practicing my web development skills.
% \end{itemize}

% Skills Section
\section*{SKILLS}
\begin{itemize}
    \item \textbf{Programming:} JavaScript/TypeScript, Python, Java, C, HTML/CSS/Sass, GDScript, PHP, MySQL, {\fontfamily{lmodern}\selectfont \LaTeX}
    \item \textbf{Software:} Familiarity with Linux, the terminal, Git/GitHub, Godot Engine
    \item \textbf{Relevant Coursework:} Intro to Algorithms, Data Structures, Linear Algebra, Statistics, etc.
    \item \textbf{General Skills:} Active listening, inclusive collaboration, problem-solving, efficiency under pressure
    \item \textbf{Languages:} Native English speaker, speaks Mandarin fluently
\end{itemize}

% End document
\end{document}
